AtmoSwing (v1.4): Analog Technique Model for Statistical Weather forecastING and downscalING

### 2016-09-22 AtmoSwing - GMD/template.tex
Adding todos.
Minor improvements of the AtmoSwing paper.

@@

\title{AtmoSwing (v1.4): Analog Technique Model for Statistical Weather downscalING}

@@

The Analog Method allows predicting local meteorological variables of interest (predictand), such as the daily precipitation, on the basis of synoptic variables (predictors). It relies on the fact that similar meteorological influences are likely to result in similar local effects. This statistical relationship is thus based on archives of observed data, and used in order to operationally forecast the coming days, or to evaluate future conditions under a changing climate.

AtmoSwing is an open source software that implements the Analog Method in a very flexible way, so that different variants can be handled dynamically, by parameterization through XML files. It is made of 3 tools: the Forecaster to perform operational forecasts, the Viewer to display the results, and the Optimizer to establish the relationship between the predictand and predictors.

@@

In addition to precipitation prediction, the Analog Method (AM), or an equivalent, was also used for short to medium term prediction of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}. \citet{Guilbaud1997} performed a literature review about the use of the AM in long-term forecasting and identified operational applications for monthly forecasts in many countries, including Canada \citep{Shabbar1986},  Hungary \citep{Toth1989}, the Netherlands \citep{Nap1981}, and England \citep{Murray1974}, as well as seasonal forecasts: \citet{Barnett1978}, \citet{Bergen1982} and \citet{Livezey1988}.

In operational forecasting, it has been used mainly by practitioners, notably hydropower companies \citep{Desaint2008a,BenDaoud2009,Obled2014} or flood forecasting services in France and Switzerland \citep{Marty2010,GarciaHernandez2009b,Horton2012}. It should however not be considered as a substitute for Numerical Weather Prediction (NWP) models, but as a complement in order to get a fast and partly independent forecast that is known to be accurate several days in advance. It therefore enriches the analysis of a potential critical situation for flood forecasting, for example, and is very interesting in early warning.

@@

\section{The Analog Method}
\label{sec:method}

@@

To get access to the frozen version at the time of writing (v1.4.2), the following address can be used:

\begin{itemize}
	\item bitbucket.org/atmoswing/atmoswing/commits/tag/1.4.2
\end{itemize}

>>>>

% TODO: read again
% TODO: add more references
% TODO: remove appendix ?
% TODO: add all reanalysis datasets
% TODO: add forecasts performances
% TODO: review: While the authors show a good command of the Analogue Technique and of its applications, it is not clear from the manuscript which predictors should be used for the forecast of alpine precipitations. The authors present two sets, that of Bontron (2004) and of Horton et al. (2012). An evaluation (or a summary, if already done elsewhere) of the relative merits of the two methods should be shown,
% TODO: relative merits of the metrics used (S1 or RMSE) are not explained
% TODO: article doesn't present any evaluation or validation of the precipitation fields/data or alerts provided by AtmoSwing
% TODO: the article is too general and descriptive and should detail the specifics of the present implementation of the Analogue Technique.
% TODO: Another point (though not a reason for rejection) is about the practical use for forecasters: as the authors rightly pointed out, it is impossible to apply analogue techniques directly on NWP forecasts of meteorological parameters, since the analogues are provided by other models, with different resolution. A coherent (I.e with the same model version and resolution) and long enough period of NWP forecasts can be hard to come by, especially for rare episodes. This may restrain the practical use of AtmoSwing for operational precipitation and flood forecasts. Maybe the authors could comment on that?

@@

\title{AtmoSwing (v1.4): Analog Technique Model for Statistical Weather forecastING and downscalING}

@@

Analog methods (AMs) allow predicting local meteorological variables of interest (predictand), such as the daily precipitation, on the basis of synoptic variables (predictors). They rely on the fact that similar meteorological influences are likely to result in similar local effects. This statistical relationship is thus based on archives of observed data, and used in order to operationally forecast the coming days, or to evaluate future conditions under a changing climate.

AtmoSwing is an open source software that implements different AM variants in a very flexible way, so that different variants can be handled dynamically, by parameterization through XML files. It is made of 3 tools: the Forecaster to perform operational forecasts, the Viewer to display the results, and the Optimizer to establish the relationship between the predictand and predictors.

@@

In addition to precipitation prediction, analog methods (AMs), or equivalent, were also used for short to medium term prediction of daily temperatures \citep{Radinovic1975, Woodcock1980, Kruizinga1983}, wind \citep{Gordon1987}, snow avalanches \citep{Obled1980, Bolognesi1993}, insolation \citep{Bois1981}, and the trajectory of tropical cyclones \citep{Keenan1981, Sievers2000, Fraedrich2003}. \citet{Guilbaud1997} performed a literature review about the use of the AM in long-term forecasting and identified operational applications for monthly forecasts in many countries, including Canada \citep{Shabbar1986},  Hungary \citep{Toth1989}, the Netherlands \citep{Nap1981}, and England \citep{Murray1974}, as well as seasonal forecasts: \citet{Barnett1978}, \citet{Bergen1982} and \citet{Livezey1988}.

In operational forecasting, they have been used mainly by practitioners, notably hydropower companies \citep{Desaint2008a,BenDaoud2009,Obled2014} or flood forecasting services in France and Switzerland \citep{Marty2010,GarciaHernandez2009b,Horton2012}. They should however not be considered as a substitute for Numerical Weather Prediction (NWP) models, but as a complement in order to get a fast and partly independent forecast that is known to be accurate several days in advance. They therefore enrich the analysis of a potential critical situation for flood forecasting, for example, and are very interesting in early warning.

@@

\section{Analog methods}
\label{sec:method}

@@

To get access to the frozen version at the time of writing (v1.4.3), the following address can be used:

\begin{itemize}
	\item bitbucket.org/atmoswing/atmoswing/commits/tag/1.4.3
\end{itemize}
